Precision calculations of the cosmic shear power spectrum projection

### 2017-02-06 limber2.tex
limber2: added text according to Peter's question about separating k and chi

The flat-sky power spectrum is
%
\begin{align}
  P_{ij}^\gamma(\ell) = & \frac 2 \pi \, \pref^2
                 \int_{0}^{\chi_{\rm lim}} {\rm d} \chi \chi \, \frac{q_i(\chi)}{a(\chi)}
                \int_{0}^{\chi_{\rm lim}} {\rm d} \chi^\prime\, \chi^\prime
                \frac{q_j(\chi^\prime)}{a(\chi^\prime)}
                \nonumber \\
                & \times \int_0^\infty {\rm d} k \, k^2 \, P_{\rm m}(k, \chi, \chi^\prime) \,
                {\rm j}_\ell(k \chi) \, {\rm j}_\ell(k \chi^\prime) .
  \label{eq:P_ell_gamma}
\end{align}
%

@@

We follow \cite{2008PhRvD..78l3506L} who derive the second-order Limber
expansion for general projections from 3D to 2D scalar fields in the spherical,
all-sky case. First, we use the identity of Bessel functions
%
\begin{equation}
  {\rm j}_\ell(x) = \sqrt{\frac{\pi}{2x}} {\rm J}_{\ell + 1/2}(x)
\end{equation}
%
in eq.~(\ref{eq:C_ell_full}). Next, \cite{2008PhRvD..78l3506L} solve
integrals of the form
%
\begin{equation}
  \int_0^\infty {\rm d} \chi f(\chi) {\rm J}_{\ell + 1/2}(k \chi)
  = \int_0^\infty {\rm d} x k^{-1} f(x/k) {\rm J}_{\ell + 1/2}(x)
  \label{eq:int_dchi}
\end{equation}
%
by performing a Taylor expansion of the function $f$ around $x = k \chi = \nu$, where
the Bessel function has its approximate maximum. To separate the $k$- and
$\chi, \chi^\prime$-terms in (\ref{eq:C_ell_full}), we first approximate the
matter power cross-spectrum between two distances as geometric mean of the two
involved distances \cite{2016arXiv161200770K}, and divide out the growth factor
to define a redshift-independent power spectrum $P_{\rm m}(k)$,
%
\begin{equation}
 P_{\rm m}(k, \chi, \chi^\prime) = \sqrt{ P_{\rm m}(k, \chi) P_{\rm m}(k, \chi^\prime) }
    =: D_+(\chi) D_+(\chi^\prime) P_{\rm m}(k).
  \label{eq:P_geom_mean}
\end{equation}
%
This is not exact, since some non-linear prescriptions of the power spectrum
depend on redshift other than the growth factor, for example when computing the
non-linear scale $k_{\rm NL}(z)$ for \texttt{halofit}.

With this, eq.~(\ref{eq:C_ell_full}) is written as
%
\begin{align}
  C^\gamma_{ij}(\ell) \approx & \, \ellbar^2(\ell, 2) \, \pref^2
                \int_0^\infty \frac{{\rm d} k}{k^3} \, P_{\rm m}(k) \,
                \int_{0}^\infty \frac{{\rm d} \chi}{\chi^{3/2}} \frac{D_+(\chi)}{a(\chi)} q_i(\chi) {\rm J}_{\ell+1/2}(k \chi)
                \nonumber \\
                 & \times
                \int_{0}^\infty \frac{{\rm d} \chi^\prime}{{\chi^\prime}^{3/2}}
                \frac{D_+(\chi^\prime)}{a(\chi^\prime)} q_j(\chi^\prime) {\rm J}_{\ell+1/2}(k \chi^\prime)
  \label{eq:C_ell_full_Pk}
\end{align}
%
We replaced the upper limits of the distance integral with infinity. \mk{Comment on this.}
Note that this equation has a preactor $\ellbar^2(\ell, 2)$ corresponding to a spin-2 field, in contrast
to \cite{2008PhRvD..78l3506L} who show calculations for a scalar field.

Following \cite{2008PhRvD..78l3506L} we expand to third order
%
\begin{equation}
  \lim_{\varepsilon \rightarrow 0} \int_0^\infty {\rm d} x \, {\rm e}^{-\epsilon (x - \nu)} g(x) {\rm J}_\nu(x)
  %\approx g(\nu) - \frac 1 2 g^{\prime\prime}(\nu) - \frac \nu 6 g^{\prime\prime\prime}(\nu) 
  \approx g(\nu) - \frac 1 2 \left.\frac{{\rm d}^2 g}{{\rm d} x^2}\right|_{x=\nu}
                 - \frac \nu 6 \left.\frac{{\rm d}^3 g}{{\rm d} x^3}\right|_(x=\nu) ,
\end{equation}
%
with $g(x) = k^{-1} f(\chi)$, $\chi=x/k$, and its derivatives $g^{(n)}(x) =
k^{-1-n} f^{(n)}(\chi)$. In our case the projection kernel is
%
\begin{equation}
  f(\chi) = D_+(\chi) a^{-1}(\chi) \chi^{-3/2} q(\chi).
  \label{eq:f_LA08}
\end{equation}
%
(Add indices $i, j$ to $f$ and $q$ for the tomographic case.)
%
Replacing both distance integrals in (\ref{eq:C_ell_full_Pk}) by their Taylor-expansions around $\nu = k \chi$ and $\nu = k \chi^\prime$,
respectively, yields
%
\begin{align}
  C^\gamma_{ij}(\ell) \approx & \, \ellbar^2(\ell, 2) \, \pref^2
    \int_0^\infty \frac{{\rm d} k}{k^3} \, P_{\rm m}(k) k^{-2}
    \left[ f_i(\chi) - \frac{1}{2 k^2} f_i^{\prime\prime}(\chi)
      - \frac{\nu}{6 k^3} f_i^{\prime\prime\prime}(\chi) + \ldots \right]
    %\nonumber \\
    %& \times
    \left[ f_j(\chi) - \frac{1}{2 k^2} f_j^{\prime\prime}(\chi)
    - \frac{\nu}{6 k^3} f_j^{\prime\prime\prime}(\chi) + \ldots \right]
  \label{eq:C_ell_limber2_dk}
\end{align}
%
Changing the integration to $\chi = \nu/k$ and collecting terms according to their $\nu$-dependence:
%
\begin{align}
  C^\gamma_{ij}(\ell) \approx & \, C^\gamma_{{\rm L1}, ij}(\ell) + C^\gamma_{{\rm L2}, ij}(\ell)
      \nonumber \\
    = & \frac{\ellbar^2(\ell, 2)}{\nu^4} \, \pref^2
    \int_0^\infty {\rm d} \chi \, \chi^3 \, P_{\rm m}\left( k \right)
    %\Bigg\{
    \left\{
    f_i(\chi) f_j(\chi)
    %\right.
      %\nonumber \\
    %&
    %\left.
     - \frac 1 {\nu^2} \left[ \frac{\chi^2}{2} \left( f^{}_i f^{\prime\prime}_j + f_i^{\prime\prime} f^{}_j \right)(\chi)
    + \frac{\chi^3}{6} \left( f^{}_i f^{\prime\prime\prime}_j + f^{\prime\prime\prime}_i f^{}_j \right)(\chi)
    \right]
    \right\}
    %\Bigg\}
  \label{eq:C_ell_limber12_dr}
\end{align}
%
The first term corresponds to the well-known first-order Limber approximation
\cite{1953ApJ...117..134L,1992ApJ...388..272K}, which is very widely used in
weak gravitational lensing. We retrieve the (spherical) standard expression by
inserting back the projection kernel (\ref{eq:f_LA08}) and the time-dependent
power spectrum,
%
\begin{align}
  C^\gamma_{{\rm L1}, ij}(\ell) = & \, \frac{\ellbar^2(\ell, 2)}{\nu^4} \, \pref^2 \int {\rm d} \chi \frac{ q_i(\chi) q_j(\chi) }{a^2(\chi)}
  P_{\rm m}\left(k = \frac{\nu}{\chi}; \chi\right).
  \label{eq:C_ell_limber1}
\end{align}
%
In the Limber approximation, modes between structures at different epochs do
not contribute to the single line-of-sight integration.

The second-order Limber term in (\ref{eq:C_ell_limber12_dr}) has an additional
$\nu^{-2}$-dependence, and is therefore strongly suppressed for large $\ell$.
%
\begin{align}
  C^\gamma_{{\rm L2}, ij}(\ell) = & - \frac 1 {\nu^2} \, \frac{\ellbar^2(\ell, 2)}{\nu^4} \, \pref^2
    \int {\rm d} \chi \, \chi^{2} a^{-2} P_{\rm m}\left(k = \frac\nu\chi; \chi\right)
    %\nonumber \\
    %& \times
    \frac 1 2 D^{-1}_+(\chi) a(\chi) \chi^{3/2} \left[ q^{}_i f^{\prime\prime}_j + f^{\prime\prime}_i q^{}_j
      + \frac{\chi}{3} \left( q^{}_i f^{\prime\prime\prime}_j + f^{\prime\prime\prime}_i q^{}_j
      \right)
    \right](\chi)
  \label{eq:C_ell_limber2_dr} 
\end{align}
%
The derivatives of the filter functions have to be computed numerically in the general case.

@@

The extended flat-sky Limber approximation is readily derived from the
spherical case, by replacing the prefactor $\ellbar^2(\ell, 2)$ with $\ell^4$,
%
\begin{align}
  P^\gamma_{{\rm L1}, ij}(\ell) = & \, \frac{\ell^4}{\nu^4} \, \pref^2 \int {\rm d} \chi \frac{ q_i(\chi) q_j(\chi) }{a^2(\chi)}
  P_{\rm m}\left(k = \frac{\nu}{\chi}; \chi\right);
  \label{eq:P_ell_limber1}
  \\
    P^\gamma_{{\rm L2}, ij}(\ell) = & - \frac 1 {\nu^2} \, \frac{\ell^4}{\nu^4} \, \pref^2
    \int {\rm d} \chi \, \chi^{2} a^{-2} P_{\rm m}\left(k = \frac\nu\chi; \chi\right)
    %\nonumber \\
    %& \times
    \frac 1 2 D^{-1}_+(\chi) a(\chi) \chi^{3/2} \left[ q^{}_i f^{\prime\prime}_j + f^{\prime\prime}_i q^{}_j  
      + \frac{\chi}{3} \left( q^{}_i f^{\prime\prime\prime}_j + f^{\prime\prime\prime}_i q^{}_j
      \right)
    \right](\chi)
  \label{eq:P_ell_limber2}
\end{align}
%
Different further approximations are commonly made for the prefactor $p(\ell) = \ell^4/\nu^4$ and $\nu(\ell)$.
%
\begin{enumerate}
  \item $p(\ell) = 1$, this corresponds to setting $\nu(\ell) = \ell$, and is the standard Limber approximation.
    Until recently, i.e.~for all pre-2014 CFHTlenS results, this was the approximation of choice.
  \item $p(\ell) = \ell^4/\nu^4(\ell)$ with $\nu(\ell) = \ell + 1/2$. This corresponds to the extended Limber
    approximation; however the following case is typically employed:
  \item $p(\ell) = 1$, but as the argument of the 3D power spectrum $\nu = \ell + 1/2$. This is a hybrid between
    standard and extended Limber approximation, and was used in \cite{KiDS-450,joudaki/etal:2016}. As is shown
    later, this is a much better approximation than case 2.
\end{enumerate}

@@

\renewcommand{\baselinestretch}{1.3}
\begin{table}[ht!]

@@

  \begin{tabular}{|l|l|c|c|c|c}
  \hline
  Case & ID & eq.~ & prefactor & $\nu(\ell)$ & Label [Comment paper] \\ \hline
  % 
  $1^{\rm st}$-order standard Limber, flat sky & L1Fl & (\ref{eq:P_ell_limber1}) + (i)
    & $1$ & $\ell$ & Kst \\ \hline
  %
  $1^{\rm st}$-order extended Limber, flat sky & ExtL1Fl & (\ref{eq:P_ell_limber1}) + (ii)
    & $\ell^4/(\ell+1/2)^4$ & $\ell + 1/2$ & ELF \\ \hline
  %
  $1^{\rm st}$-order extended Limber, hybrid, flat sky & ExtL1FlHyb & (\ref{eq:P_ell_limber1}) + (iii)
    & $1$ & $\ell + 1/2$ & ESt \\ \hline
  %
  $1^{\rm st}$-order extended Limber, spherical & ExtL1Sph & (\ref{eq:C_ell_limber1})
    & $\ellbar^2(\ell, 2)/(\ell+1/2)^4$ & $\ell+1/2$ & ELS \\ \hline
  %
  $2^{\rm st}$-order extended Limber, flat sky & Ext2FlHyb & (\ref{eq:P_ell_limber2}) + (iii)
    & $\ellbar^2(\ell, 2)/(\ell+1/2)^4$ & $\ell+1/2$ & - \\ \hline
  %
  $2^{\rm st}$-order extended Limber, spherical & Ext2Sph & (\ref{eq:C_ell_limber1})+(\ref{eq:C_ell_limber2_dr})
    & $\ellbar^2(\ell, 2)/(\ell+1/2)^4$ & $\ell+1/2$ & - \\ \hline
  %
  Full spherical & FullSph & (\ref{eq:C_ell_full}) &
      $\ellbar^2(\ell, 2)$ & - & - \\ \hline
  %
  \end{tabular}

@@

We run various projection modes on CFHTLenS single-redshift bin data
\cite{CFHTLenS-2pt-notomo}. The setting is exactly the same as for the 2013
results. Note that since then many improvements have been obtained, those
results do not reflect the most up-to-date cosmological constraints. This is
sufficient however for our purpose to show the effect of projection
approximations for weak-lensing surveys. Thos improvement have been made on the
theoretical modelling side (revised non-linear power spectrum
\cite{2012ApJ...761..152T}, baryonic modifications of the total power spectrum
\cite{2015MNRAS.454.1958M}), and the data processing (photometric redshifts
\cite{2016MNRAS.463.3737C,joudaki/etal:2016}, shear calibration
\cite{KiDS-450}, Fenech Compti). The state-of-the-art cosmological constraints
for CFHTLenS including most of those updates are presented in
\cite{joudaki/etal:2016}.

@@

The PhD thesis of Van de Rijt \cite{vande2012} presents an explicit calculation
of the second-order Limber approximation for a fixed source redshift. They
carry out the derivatives of the kernels $f$ under the assumption of a constant
growth-suppression factor $D_+(a)/a$. We show the consistency between their
result (eq.~7.19) and our (\ref{eq:C_ell_limber2_dr}), as follows.

>>>>

The flat-sky power spectrum is
%
\begin{align}
  P_{ij}^\gamma(\ell) = & \frac 2 \pi \, \pref^2
                 \int_{0}^{\chi_{\rm lim}} {\rm d} \chi \chi \, \frac{q_i(\chi)}{a(\chi)}
                \int_{0}^{\chi_{\rm lim}} {\rm d} \chi^\prime\, \chi^\prime
                \frac{q_j(\chi^\prime)}{a(\chi^\prime)}
                \nonumber \\
                & \times \int_0^\infty {\rm d} k \, k^2 \, P_{\rm m}(k; \chi, \chi^\prime) \,
                {\rm j}_\ell(k \chi) \, {\rm j}_\ell(k \chi^\prime) .
  \label{eq:P_ell_gamma}
\end{align}
%

@@

We follow \cite{2008PhRvD..78l3506L} who derive the second-order Limber
expansion for general projections from 3D to 2D scalar fields in the spherical,
all-sky case. First, we use the identity of Bessel functions
%
\begin{equation}
  {\rm j}_\ell(x) = \sqrt{\frac{\pi}{2x}} {\rm J}_{\ell + 1/2}(x)
\end{equation}
%
in eq.~(\ref{eq:C_ell_full}). Next, \cite{2008PhRvD..78l3506L} solve
integrals of the form
%
\begin{equation}
  \int_0^\infty {\rm d} \chi f(\chi) {\rm J}_{\ell + 1/2}(k \chi)
  = \int_0^\infty {\rm d} x k^{-1} f(x/k) {\rm J}_{\ell + 1/2}(x)
  \label{eq:int_dchi}
\end{equation}
%
by performing a Taylor expansion of the function $f$ around $x = k \chi = \nu$, where
the Bessel function has its approximate maximum.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Geometric mean cross-correlation power spectrum}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

To separate the $k$- and $\chi, \chi^\prime$-terms in (\ref{eq:C_ell_full}), we
first approximate the matter power cross-spectrum between two distances as
geometric mean of the two involved distances \cite{2005PhRvD..72b3516C,2016arXiv161200770K},
%
\begin{equation}
 P_{\rm m}(k; \chi, \chi^\prime) = \sqrt{ P_{\rm m}(k; \chi) P_{\rm m}(k; \chi^\prime) }
  \label{eq:P_geom_mean}
\end{equation}
%
With this, eq.~(\ref{eq:C_ell_full}) is written as
%
\begin{align}
  C^\gamma_{ij}(\ell) \approx & \, \ellbar^2(\ell, 2) \, \pref^2
                \int_0^\infty \frac{{\rm d} k}{k^3} \,
                % P_{\rm m}(k) \,
                \int_{0}^\infty \frac{{\rm d} \chi}{\chi^{3/2}} \sqrt{P_{\rm m}(k; \chi)}
                \frac{q_i(\chi)}{a(\chi)} {\rm J}_{\ell+1/2}(k \chi)
                \nonumber \\
                 & \times
                \int_{0}^\infty \frac{{\rm d} \chi^\prime}{{\chi^\prime}^{3/2}}
                \sqrt{P_{\rm m}(k; \chi^\prime)} \frac{q_j(\chi^\prime)}{a(\chi^\prime)} {\rm J}_{\ell+1/2}(k \chi^\prime)
  \label{eq:C_ell_full_Pk}
\end{align}
%
We replaced the upper limits of the distance integral with infinity. \mk{Comment on this.}
Note that this equation has a preactor $\ellbar^2(\ell, 2)$ corresponding to a spin-2 field, in contrast
to \cite{2008PhRvD..78l3506L} who show calculations for a scalar field.

Following \cite{2008PhRvD..78l3506L} we expand to third order
%
\begin{equation}
  \lim_{\varepsilon \rightarrow 0} \int_0^\infty {\rm d} x \, {\rm e}^{-\epsilon (x - \nu)} g(x) {\rm J}_\nu(x)
  %\approx g(\nu) - \frac 1 2 g^{\prime\prime}(\nu) - \frac \nu 6 g^{\prime\prime\prime}(\nu) 
  \approx g(\nu) - \frac 1 2 \left.\frac{{\rm d}^2 g}{{\rm d} x^2}\right|_{x=\nu}
                 - \frac \nu 6 \left.\frac{{\rm d}^3 g}{{\rm d} x^3}\right|_{x=\nu} ,
\end{equation}
%
with $g(x) = k^{-1} f(k, \chi)$, $\chi=x/k$, and its derivatives $g^{(n)}(x) =
k^{-1-n} f^{(n)}(k, \chi)$ for a given $k$. In our case the projection kernel is
%
\begin{equation}
  f(k, \chi) = \sqrt{P_{\rm m}(k; \chi)} \, a^{-1}(\chi) \chi^{-3/2} q(\chi).
  \label{eq:f_LA08}
\end{equation}
%
(Add indices $i, j$ to $f$ and $q$ for the tomographic case.)
%
Replacing both distance integrals in (\ref{eq:C_ell_full_Pk}) by their Taylor-expansions around $\nu = k \chi$ and $\nu = k \chi^\prime$,
respectively, yields
%
\begin{align}
  C^\gamma_{ij}(\ell) \approx & \, \ellbar^2(\ell, 2) \, \pref^2
    \int_0^\infty \frac{{\rm d} k}{k^3} \, k^{-2}
    \left[ f_i(k, \chi) - \frac{1}{2 k^2} f_i^{\prime\prime}(k, \chi)
      - \frac{\nu}{6 k^3} f_i^{\prime\prime\prime}(k, \chi) + \ldots \right]
    %\nonumber \\
    %& \times
    \left[ f_j(k, \chi) - \frac{1}{2 k^2} f_j^{\prime\prime}(k, \chi)
    - \frac{\nu}{6 k^3} f_j^{\prime\prime\prime}(k, \chi) + \ldots \right]
  \label{eq:C_ell_limber2_dk}
\end{align}
%
Changing the integration to $\chi = \nu/k$ and collecting terms according to their $\nu$-dependence:
%
\begin{align}
  C^\gamma_{ij}(\ell) \approx & \, C^\gamma_{{\rm L1}, ij}(\ell) + C^\gamma_{{\rm L2}, ij}(\ell)
      \nonumber \\
    = & \frac{\ellbar^2(\ell, 2)}{\nu^4} \, \pref^2
    \int_0^\infty {\rm d} \chi \, \chi^3 \, % P_{\rm m}\left( k \right)
    %\Bigg\{
    \left\{
    (f_i f_j)(\nu/\chi, \chi)
    %\right.
      %\nonumber \\
    %&
    %\left.
     - \frac 1 {\nu^2} \left[ \frac{\chi^2}{2} \left( f^{}_i f^{\prime\prime}_j + f_i^{\prime\prime} f^{}_j \right)(\nu/\chi, \chi)
    + \frac{\chi^3}{6} \left( f^{}_i f^{\prime\prime\prime}_j + f^{\prime\prime\prime}_i f^{}_j \right)(\nu/\chi, \chi)
    \right]
    \right\}
    %\Bigg\}
  \label{eq:C_ell_limber12_dr}
\end{align}
%
The first term corresponds to the well-known first-order Limber approximation
\cite{1953ApJ...117..134L,1992ApJ...388..272K}, which is very widely used in
weak gravitational lensing. We retrieve the (spherical) standard expression by
inserting back the projection kernel (\ref{eq:f_LA08}) and the time-dependent
power spectrum,
%
\begin{align}
  C^\gamma_{{\rm L1}, ij}(\ell) = & \, \frac{\ellbar^2(\ell, 2)}{\nu^4} \, \pref^2 \int {\rm d} \chi \frac{ q_i(\chi) q_j(\chi) }{a^2(\chi)}
  P_{\rm m}\left(\frac{\nu}{\chi}; \chi\right).
  \label{eq:C_ell_limber1}
\end{align}
%
In the Limber approximation, modes between structures at different epochs do
not contribute to the single line-of-sight integration.

The second-order Limber term in (\ref{eq:C_ell_limber12_dr}) has an additional
$\nu^{-2}$-dependence, and is therefore strongly suppressed for large $\ell$.
%
\begin{align}
  C^\gamma_{{\rm L2}, ij}(\ell) = & - \frac 1 {\nu^2} \, \frac{\ellbar^2(\ell, 2)}{\nu^4} \, \pref^2
    \int {\rm d} \chi \, \chi^{2} a^{-2} \sqrt{P_{\rm m}\left(\frac\nu\chi; \chi\right)}
    %\nonumber \\
    %& \times
    \frac{a(\chi)}{2} \chi^{3/2} \left[ q^{}_i f^{\prime\prime}_j + f^{\prime\prime}_i q^{}_j
      + \frac{\chi}{3} \left( q^{}_i f^{\prime\prime\prime}_j + f^{\prime\prime\prime}_i q^{}_j
      \right)
    \right](\nu/\chi, \chi)
  \label{eq:C_ell_limber2_dr} 
\end{align}
%
The higher-order derivatives of the filter functions have to be computed
numerically in the general case. These suffer from numerical noise and are
sensitive to the set-up, for example the step size. The tabulation and
interpolation of those derivatives is time-taking since they depend on two
arguments, $\nu$ and $\chi$. In the following section, we will separate the
$k$- and $\chi$-dependend parts of the power spectrum to make the numerical
derivatives faster and more smooth.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Time-independent power spectrum separation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

To further develop (\ref{eq:P_geom_mean}), we divide out the growth factor to
define a redshift-independent power spectrum $P_{\rm m}(k)$,
%
\begin{equation}
 P_{\rm m}(k, \chi) =: D_+(\chi) P_{\rm m}(k).
  \label{eq:P_k_chi_sep_s}
\end{equation}
%
This is not exact, since some non-linear prescriptions of the power spectrum
depend on redshift other than the growth factor, for example when computing the
non-linear scale $k_{\rm NL}(z)$ for \texttt{halofit}.

With this approximation, the $k$-independent term factors out
from (\ref{eq:f_LA08}), and we define the separated kernel function $f_{\rm s}$ as
%
\begin{equation}
  f_{\rm s}(\chi) = \sqrt{P_{\rm m}(k)} D_+(\chi) a^{-1}(\chi) \chi^{-3/2} q(\chi).
  \label{eq:f_LA08_s}
\end{equation}
%
and does not need to be considered when taking the derivatives with respect to comoving distances.
The second-order Limber term of the shear power spectrum can then be simplified to
%
\begin{align}
  C^\gamma_{{\rm L2}, ij}(\ell) = & - \frac 1 {\nu^2} \, \frac{\ellbar^2(\ell, 2)}{\nu^4} \, \pref^2
    \int {\rm d} \chi \, \chi^{2} a^{-2} P_{\rm m}\left(\frac\nu\chi; \chi\right)
    %\nonumber \\
    %& \times
    \frac {a(\chi)}{2 D_+(\chi)} \chi^{3/2}
    \left[ q^{}_i f^{\prime\prime}_{{\rm s} j} + f^{\prime\prime}_{{\rm s}i} q^{}_j
      + \frac{\chi}{3} \left( q^{}_i f^{\prime\prime\prime}_{{\rm s}j} + f^{\prime\prime\prime}_{{\rm s}i} q^{}_j
      \right)
    \right](\chi)
  \label{eq:C_ell_limber2_dr_s}
\end{align}
%
We compute the numerical higher derivatives as follows. The functions $f_{\rm
s}(\chi)$ are fitted as power laws with index $\approx 1.5$. The fit is
performed between $\chi_{\rm min} = 0.001 {\rm Mpc}/h$ and $\chi_{\rm max} =
500 \mbox{Mpc}/h$. At larger comoving distances the kernel decreases faster
than a power law, so we exclude this range from the fit. Even though the
derivaties are larger due to the steeper decline, the associated errors are
very small since those scales are down-weighed by the kernel function $f_{\rm
s}$ itself. At $\chi = 500 \mbox{Mpc}/h$ the filter function is less than
$10^{-4}$ of its value of unity at Mpc$/h$.

%The error between filter and power-law fit
%becomes larger than $50\%$ only for scales larger than $1,500 \mbox{Mpc}/h$. On the angular
%scales where the second-order Limber approximation significantly contributes to the shear
%power spectrum, $\ell \le 100$, this corresponds to $k < 0.03 h/$Mpc, linear
%scales where the 3D power spectrum is small and does not strongly contribute to the lensing
%power spectrum.

@@

The extended flat-sky Limber approximation is readily derived from the
spherical case, by replacing the prefactor $\ellbar^2(\ell, 2)$ with $\ell^4$,
%
\begin{align}
  P^\gamma_{{\rm L1}, ij}(\ell) = & \, \frac{\ell^4}{\nu^4} \, \pref^2 \int {\rm d} \chi \frac{ q_i(\chi) q_j(\chi) }{a^2(\chi)}
  P_{\rm m}\left(k = \frac{\nu}{\chi}; \chi\right);
  \label{eq:P_ell_limber1}
  \\
    P^\gamma_{{\rm L2}, ij}(\ell) = & - \frac 1 {\nu^2} \, \frac{\ell^4}{\nu^4} \, \pref^2
    \int {\rm d} \chi \, \chi^{2} a^{-2} P_{\rm m}\left(k = \frac\nu\chi; \chi\right)
    %\nonumber \\
    %& \times
    \frac{a(\chi)}{2 D^{-1}_+(\chi)} \chi^{3/2} \left[ q^{}_i f^{\prime\prime}_{{\rm s}j} + f^{\prime\prime}_{{\rm s}i} q^{}_j  
      + \frac{\chi}{3} \left( q^{}_i f^{\prime\prime\prime}_{{\rm s}j} + f^{\prime\prime\prime}_{{\rm s}i} q^{}_j
      \right)
    \right](\chi)
  \label{eq:P_ell_limber2}
\end{align}
%
Different further approximations are commonly made for the prefactor $p(\ell) = \ell^4/\nu^4$ and $\nu(\ell)$.
%
\begin{enumerate}
  \item $p(\ell) = 1$, this corresponds to setting $\nu(\ell) = \ell$, and is the standard Limber approximation.
    Until recently, i.e.~for all pre-2014 CFHTlenS results, this was the approximation of choice.
  \item $p(\ell) = \ell^4/\nu^4(\ell)$ with $\nu(\ell) = \ell + 1/2$. This corresponds to the extended Limber
    approximation; however the following case is typically employed:
  \item $p(\ell) = 1$, but as the argument of the 3D power spectrum $\nu = \ell + 1/2$. This is a hybrid between
    standard and extended Limber approximation, and was used in \cite{KiDS-450,joudaki/etal:2016}. As is shown
    later, this is a much better approximation than case 2.
\end{enumerate}

@@

\renewcommand{\baselinestretch}{1.3}
\begin{table}

@@

  \begin{tabular}{|l|l|c|c|c|c}
  \hline
  Case & ID & eq.~ & prefactor & $\nu(\ell)$ & Label [Comment paper] \\ \hline
  % 
  $1^{\rm st}$-order standard Limber, flat sky & L1Fl & (\ref{eq:P_ell_limber1}) + (i)
    & $1$ & $\ell$ & Kst \\ \hline
  %
  $1^{\rm st}$-order extended Limber, flat sky & ExtL1Fl & (\ref{eq:P_ell_limber1}) + (ii)
    & $\ell^4/(\ell+1/2)^4$ & $\ell + 1/2$ & ELF \\ \hline
  %
  $1^{\rm st}$-order extended Limber, hybrid, flat sky & ExtL1FlHyb & (\ref{eq:P_ell_limber1}) + (iii)
    & $1$ & $\ell + 1/2$ & ESt \\ \hline
  %
  $1^{\rm st}$-order extended Limber, spherical & ExtL1Sph & (\ref{eq:C_ell_limber1})
    & $\ellbar^2(\ell, 2)/(\ell+1/2)^4$ & $\ell+1/2$ & ELS \\ \hline
  %
  $2^{\rm st}$-order extended Limber, flat sky & Ext2FlHyb &  (\ref{eq:P_ell_limber1}) + (\ref{eq:P_ell_limber2}) + (iii)
    & $\ellbar^2(\ell, 2)/(\ell+1/2)^4$ & $\ell+1/2$ & - \\ \hline
  %
  $2^{\rm st}$-order extended Limber, spherical & Ext2Sph & (\ref{eq:C_ell_limber1})+(\ref{eq:C_ell_limber2_dr_s})
    & $\ellbar^2(\ell, 2)/(\ell+1/2)^4$ & $\ell+1/2$ & - \\ \hline
  %
  Full spherical & FullSph & (\ref{eq:C_ell_full}) &
      $\ellbar^2(\ell, 2)$ & - & - \\ \hline
  %
  \end{tabular}

@@

We run various projection modes on CFHTLenS single-redshift bin data
\cite{CFHTLenS-2pt-notomo}. The setting is exactly the same as for the 2013
results. Note that since then many improvements have been obtained, those
results do not reflect the most up-to-date cosmological constraints. This is
sufficient however for our purpose to show the effect of projection
approximations for weak-lensing surveys. Thos improvement have been made on the
theoretical modelling side (revised non-linear power spectrum
\cite{2012ApJ...761..152T}, baryonic modifications of the total power spectrum
\cite{2015MNRAS.454.1958M}), and the data processing (photometric redshifts
\cite{2016MNRAS.463.3737C,joudaki/etal:2016}, shear calibration
\cite{KiDS-450}, Fenech Compti). The state-of-the-art cosmological constraints
for CFHTLenS including most of those updates are $\sigma_8 (\Omega_{\rm
m}/0.3)^{0.4} = 0.78\pm{0.04}$, presented in \cite{joudaki/etal:2016}.

@@

The PhD thesis of Van de Rijt \cite{vande2012} presents an explicit calculation
of the second-order Limber approximation for a fixed source redshift. They
carry out the derivatives of the kernels $f$ under the assumption of a constant
growth-suppression factor $D_+(a)/a$, and a power spectrum that separates $k$-
from $\chi$-terms. We show the consistency between their result (eq.~7.19) and
our (\ref{eq:C_ell_limber2_dr_s}), as follows.

We write (\ref{eq:C_ell_limber2_dr_s}) without tomography, and insert again the
time-independent power spectrum (\ref{eq:P_geom_mean}),
%
\begin{align}
  C^\gamma_{{\rm L2}}(\ell) = & - \frac 1 {\nu^2} \, \frac{\ellbar^2(\ell, 2)}{\nu^4} \, \pref^2
    \int {\rm d} \chi \, \chi^{2} P_{\rm m}\left(k = \frac\nu\chi\right)
    \nonumber \\
    & \times D_+(\chi) a^{-1}(\chi) \chi^{3/2} q(\chi) \left[ f^{\prime\prime} 
      + \frac{\chi}{3} f^{\prime\prime\prime} 
    \right](\chi)
  \label{eq:C_ell_limber2_dr_notomo}
\end{align}
%
For a fixed source comoving distance $\chi_{\rm S}$ the lensing efficiency is
$q(\chi) = (\chi_{\rm S} - \chi) \chi_{\rm S}^{-1}$. Assuming that
$D_+(\chi)/a(\chi) \approx g = \mbox{const}$, we get for the derivative terms,
with $f(\chi) = g \chi_{\rm S}^{-1} (\chi_{\rm S} - \chi) \chi^{-3/2}$,
%
\begin{equation}
  f^{\prime\prime}(\chi) + \frac{\chi}{3} f^{\prime\prime\prime}(\chi)
    = - \frac 1 8 \chi^{-5/2} \left( \frac 5 \chi
          + \frac 1 {\chi_{\rm S}} \right) \frac{D_+(\chi)}{a(\chi)}.
\end{equation}
%
Therefore,
%
\begin{align}
  C^\gamma_{{\rm L2}}(\ell) = \frac 1 {\nu^2} \, \frac{\ellbar^2(\ell, 2)}{\nu^4} \, \pref^2
    \int {\rm d} \chi \, \chi \, P_{\rm m}\left(k = \frac\nu\chi\right)
    \frac{q(\chi)}{8} \left( \frac 5 \chi + \frac 1 {\chi_{\rm S}} \right)
      \left(\frac{D_+(\chi)}{a(\chi)}\right)^2 
\end{align}
%
We now replace the matter with the potential power spectrum, ${\cal A}^2 P_{\rm m}(k) = k^{4} a^2 P_\Phi(k)$, and pull into the integral $\nu^{-4} = \chi^{-4} k^{-4}$. This yields
%
\begin{align}
  C^\gamma_{{\rm L2}}(\ell) = \frac 1 {\nu^2} \, \ellbar^2(\ell, 2)
    \int \frac{{\rm d} \chi}{\chi^2} \, P_\Phi\left(k = \frac\nu\chi\right)
    a^2(\chi) \frac{1}{8} \frac{\chi_{\rm S} - \chi}{\chi \chi_{\rm S}}
    \left( \frac 5 \chi + \frac 1 {\chi_{\rm S}} \right)
      \left(\frac{D_+(\chi)}{a(\chi)}\right)^2 .
\end{align}
%
Note the additional factor $a^2(\chi)$. This difference is accounted for by the
factor $a^{-1}$ in the propagation of primordial potential perturbations to
late times, see eq.~(6.22) in \cite{vande2012}, where the transition is done
using $g(a)$ instead of $D(a)$. \mk{Check this further.}
